Maps

### 2020-05-05 ms_8.Rmd
Commit plan z, png maps

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
#library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)
library(readxl)
library(gganimate)
library(patchwork)
library(magick)
library(webshot)
webshot::install_phantomjs()

@@

@@

@@

leaflet(countyyear) %>%
  addTiles() %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.3, fillOpacity = 1,
              fillColor = ~pal(myvariable)) %>%
  addLegend(pal = pal, values = ~myvariable, opacity = 1.0, title = myvar)

@@

@@

```{r mwData-shapefile-merger}
# NEW tibble
# columns: COUNTYA?, YEAR, variable, value

@@

mapData <- left_join(mapData1, shapefiles, by = c("YEAR" = "Year"))

@@

@@

@@

>>>>

library(shiny)
library(haven)
library(tidyverse)
library(gt)
library(devtools)
library(tibble)
#library(foreign)
library(scales)
library(shinythemes)
library(plotly)
library(leaflet)
library(broom)
library(readxl)
library(gganimate)
library(patchwork)
library(magick)
library(webshot)
library(mapview)
# Probably not necessary
#webshot::install_phantomjs()

@@

# myvar options will be determined by column names of appPlan & displayed via dropdown widget
myvar <- "Average Implement Value"

@@

#countyyear <- rmapshaper::ms_simplify(countyyear)

@@

leaflet(countyyear) %>%
  addTiles() %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.3, fillOpacity = 1,
              fillColor = ~pal(myvariable)) %>%
  #setView(-87.4290, 43, zoom = 6) %>%
  addLegend(pal = pal, values = ~myvariable, opacity = 1.0, title = myvar)

@@

```{r}
# Saving maps as pngs
# Since I couldn't get my interactive maps to run on shiny, this is the supremely disappointing 
# work-around

## 'leaflet' objects (image above)

# mapshot(enroll_1870, file = "enroll_1870.png")

# This initially worked, but then R started crashing every time I tried to run it
# Now I'm resorting to sCreEnsHotS

# SCREENSHOT Section
# Delete later

```{r}
year <- 1880

# myvar options will be determined by column names of appPlan & displayed via dropdown widget
myvar <- "Average Implement Value"

#countyyear <- rmapshaper::ms_simplify(countyyear)

leaflet(countyyear) %>%
  addTiles() %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.3, fillOpacity = 1,
              fillColor = ~pal(myvariable)) %>%
  #setView(-87.4290, 43, zoom = 6) %>%
  addLegend(pal = pal, values = ~myvariable, opacity = 1.0, title = myvar)
```

```{r}
year <- 1890

# myvar options will be determined by column names of appPlan & displayed via dropdown widget
myvar <- "Average Implement Value"

#countyyear <- rmapshaper::ms_simplify(countyyear)

leaflet(countyyear) %>%
  addTiles() %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.3, fillOpacity = 1,
              fillColor = ~pal(myvariable)) %>%
  #setView(-87.4290, 43, zoom = 6) %>%
  addLegend(pal = pal, values = ~myvariable, opacity = 1.0, title = myvar)
```

@@

```{r mwData-shapefile-merger}

# Ultimately, this didn't work
# I'm giving up and saving individual leaflets as

# NEW tibble
# columns: COUNTYA?, YEAR, variable, value

# Plan: make the huge sf object for each variable from 1870-1890
# bind all the rows
# it will be huge
# save as rds
# read in at the beginning, just filter by year and variable, which now each have their own column
# figure out how to get widgets to work

@@

mapData <- left_join(mapData1, shapefiles, by = c("YEAR" = "Year")) %>%

  # Only do the first three decades
  # Shiny doesn't give you enough space to upload the rest anyway

  filter(YEAR == "1870" | YEAR == "1880" | YEAR == "1890")

@@

dsnyear <- datayear %>% 
  slice(1) %>% 
  pull(Dsn)

layeryear <- datayear %>% 
  slice(1) %>% 
  pull(Layer)

@@

countyyear1 <- rmapshaper::ms_simplify(countyyear)

@@

# myvar options will be determined by column names of appPlan & displayed via dropdown widget
myvar <- "Average Farm Value"

datayear <- mapData %>%
  # use get() to use the stored variable
  # idk why, but it doesn't work without this
  # the variable must be converted to a double in the original mwData dataset
  filter(YEAR == year) %>%
  select(GISJOIN, YEAR, Variable, value, Dsn, Layer)

dsnyear <- datayear %>% 
  slice(1) %>% 
  pull(Dsn)

layeryear <- datayear %>% 
  slice(1) %>% 
  pull(Layer)

# make a huge sf object that has all of the info
# save as RDS
# use only one filter (for year and variable) with the code calling the palette and below

# Condense size of data for faster processing
# This is taking too long to run; session encounters a fatal error
# What if I simplify after filtering?
# countyyear <- rmapshaper::ms_simplify(countyyear)

countyear <- countyyear %>%
  filter(Variable == myvar)

leaflet(countyyear) %>%
  addTiles() %>%
  addPolygons(stroke = FALSE, smoothFactor = 0.3, fillOpacity = 1,
              fillColor = ~pal(value)) %>%
  #setView(-87.4290, 43, zoom = 6) %>%
  addLegend(pal = pal, values = ~value, opacity = 1.0, title = myvar)
